Using Graphical Models for Novelty Detection on Semantic Room Classification

### 2011-05-09 semantic-nd/article.tex
some cleanup on what to write on each section and added dummy images.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{itemize}
\item Explain context of indoor room categorization and importance of novelty detection.
\item Introduce Dora and explain how it would benefit or use the semantic novel detection.
\end{itemize}

There has been several efforts in the area of Artificial Intelligence and Robotics in creating
robots that are able to interact with humans and their environments.
One of the existing problems is a reliable high-level localization method that can be deployed
into new and unknown environments.
This article focus on the mapping, using \emph{semantic data}, of indoor environments such as
houses and offices to room categories such as kitchen, corridor, office.
And how to perform novelty detection on them: \emph{detect a new room category that was not
present in the labelled data}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dora Architecture Overview}
\begin{itemize}
\item Introduce Dora architecture aspects important for the paper
\item Explain what we mean by semantic data and how its captured by Dora
\item Introduce graphical models and how we use them (including notation on the paper)
\end{itemize}

Short paragraph describing dora. Short paragraph describing dora. Short paragraph describing dora. Short paragraph describing dora. Short paragraph describing dora.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novelty Detection}
\begin{itemize}
\item Define novelty detection 
\item Explain approach with a threshold function
\item Need of a normalizing factor for a threshold with dynamic functions
\item Usage of conditional density
\item Assuming of every output is equally likely
\item Using unlabelled data
\end{itemize}

% Introduce novelty detection
Novelty detection is an harder problem than that of classification due to its single-class nature.
Essentially a system is given training data and when given new data has to decide if it belongs
to the same concept it was trained with.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\begin{itemize}
\item Show results and how much it improves by using a simple method for unconditional probability
\end{itemize}

In order to verify the improvements obtained by using unlabelled data, a fictitious simple
dataset was generated.
The fictitious distribution assumes that an independent and variable size set of features
$x$ is generated by a given room category.
In whole there was 11 different room categories and 7 different measured properties types.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{figures/roc-simple.pdf}

@@

\begin{figure}
\centering

\subfloat[3 sensed variables]{5 sensed variables}
\qquad
\subfloat[5 sensed variables]{5 sensed variables}

\subfloat[10 sensed variables]{10 sensed variables}
\qquad
\subfloat[50 sensed variables]{50 sensed variables}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\begin{itemize}
\item Show a correct estimation of unconditional probability to be important in establishing a novelty detection threshold
\item Show unlabelled data can be used for it.
\item Although focus on Room Categorization we expect the results and techniques to be usable on other areas.
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
There has been several efforts in the area of Artificial Intelligence and Robotics in creating
robots that are able to interact with humans and their environments.
One of the existing problems is a reliable high-level localization method that can be deployed
into new and unknown environments.
This article focus on the mapping, using \emph{semantic data}, of indoor environments such as
houses and offices to room categories such as kitchen, corridor, office.
And how to perform novelty detection on them: \emph{detect a new room category that was not
present in the labelled data}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dora Architecture Overview}
Short paragraph describing dora. Short paragraph describing dora. Short paragraph describing dora. Short paragraph describing dora. Short paragraph describing dora.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novelty Detection}
% Introduce novelty detection
Novelty detection is an harder problem than that of classification due to its single-class nature.
Essentially a system is given training data and when given new data has to decide if it belongs
to the same concept it was trained with.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
In order to verify the improvements obtained by using unlabelled data, a fictitious simple
dataset was generated.
The fictitious distribution assumes that an independent and variable size set of features
$x$ is generated by a given room category.
In whole there was 11 different room categories and 7 different measured properties types.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}

@@

\subfloat[3 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}
\qquad
\subfloat[5 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}

\subfloat[10 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}
\qquad
\subfloat[50 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
